### 2013-07-24 doc/asplos14/evaluation.tex
remove UPC from places it doesnt belong

In order to put \Grappa's performance into a general context, we compare it
with XMT running BFS, PageRank, IntSort, GUPS and UTS. Since XMT is a
different hardware platform, we also compare \Grappa with optimized MPI
versions of BFS and GUPS running on the same hardware. Finally, we also
compare it with UTS written for UPC. We run all experiments with 64 nodes and 16 cores per node.

@@

We also compare with an UPC UTS implementation, which is nearly 10$\times$
\emph{slower} than \Grappa. Our UPC version supports work-stealing but has
limited ability to overlap communication with computation. Also, it
employs heavyweight synchronization operations when stealing. \Grappa
benefits from its lightweight context switching and support for fine-grained
synchronization.

>>>>

In order to put \Grappa's performance into a general context, we compare it
with XMT running BFS, PageRank, IntSort, GUPS and UTS. Since XMT is a
different hardware platform, we also compare \Grappa with optimized MPI
versions of BFS and GUPS running on the same hardware. We run all experiments with 64 nodes and 16 cores per node.

@@

%bdmyers: the below is already covered specially in the UTS section
%We also compare with an UPC UTS implementation, which is nearly 10$\times$
%\emph{slower} than \Grappa. Our UPC version supports work-stealing but has
%limited ability to overlap communication with computation. Also, it
%employs heavyweight synchronization operations when stealing. \Grappa
%benefits from its lightweight context switching and support for fine-grained
%synchronization.
